Improving the Replicability of Psychological Science Through Pedagogy

### 2017-06-26 paper/paper.Rmd
Intro and start to new discussion

In the current article, we report the results of replication projects conducted in a single class (a graduate-level experimental methods course). As part of the required work of the course, students conducted replications of published articles from the 2015 volume of the journal *Psychological Science*. These studies give evidence about the state of replicability in the field. They also provide insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.

Past work has explicitly attempted to estimate the proportion of true effects in a particular literature [@ioannidis2005;@osc2015], but this goal is challenging -- perhaps even impossible [@gilbert2016;@anderson2016]. Presupposing that this construct is even meaningful [cf. @gergen1973], assessing the truth of even an individual effect relies on delineating what constitutes an exact replication [e.g., @stroebe2014] and establishing a standard for replication success [e.g., @simonsohn2015]. Estimating the proportion of true effects in a literature further requires a systematic sampling strategy to ensure generality. Furthermore, no single replication attempt is definitive, so multiple iterations are typically necessary to increase the evidential value of replication attempts [@lewis2016;@klein2014;@wagenmakers2016].

In the current work, we do not address these issues; instead, our goal is more modest. We assess the challenges facing a student in choosing an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproducing the findings. We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations. While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work. But, as we discuss below, the results of these replications may have different interpretations: While some are more direct, others differ on theoretically-relevant dimensions. Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing the boundary conditions of a particular effect rather than replicating the original exactly. Even in these cases, however, replication research of the type we conduct here contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.

@@

We begin by describing the details of our course projects. Below, in the subsection on Pedagogical Implications, we discuss broader decision points for the course design that other instructors might consider.

@@

All study participants were recruited on AMT. Individual sample sizes are given in Table \ref{tab:summary}. Each sample was recruited independently, using the same account but a different title. Of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on AMT. For the other studies in our sample, demographic differences (in terms of age, sex, socio-economic status, and in some cases, national origin) are an important factor in interpreting our findings; see Supplemental Material for more discussion of this issue in individual cases.

@@

HOW CAN THIS BE GENERALIZED

>>>>

In the current article, we address the practical barriers of completing replcations as part of required coursework and discuss the methodological decisions that replication projects must address more braodly.  Towards this aim, report the results of replication projects conducted in a graduate-level experimental methods course. Students conducted replications of published articles from the 2015 volume of the journal *Psychological Science*. These studies provide insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.

We assess the challenges facing a student in choosing an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproducing the findings. We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations. While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work. But, as we discuss below, the results of these replications may have different interpretations: While some are more direct, others differ on theoretically-relevant dimensions. Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing the boundary conditions of a particular effect rather than replicating the original exactly. Even in these cases, however, replication research of the type we conduct here contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.

@@

We begin by describing the details of our course projects to give a sense of what a classroom replication project entails. We then discuss broader decision points for the course design that other instructors might consider. Lastly, we report the results our replications, highlighting the importance of wide-scale replication.

@@

All study participants were recruited on Amazon Mechanical Turk (AMT). Individual sample sizes are given in Table \ref{tab:summary}. Each sample was recruited independently, using the same account but a different title. Of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on AMT. For the other studies in our sample, demographic differences (in terms of age, sex, socio-economic status, and in some cases, national origin) are an important factor in interpreting our findings; see Supplemental Material for more discussion of this issue in individual cases.

@@

Above we have shown that classroom replication projects are possible. We now present information that we hope will reduce barriers to entry and encourage more researchers and instructor to include replications as part of course work.  This includes practical recommendations for implementation in a variety of classroom, key decision that instructors must make, and common issues that may arise throughout the projects and ways to mitigate or prevent these issues.
